Additional analyses

### 2022-04-12 analyses.RmD
- implented reviewer feedback

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey60", "grey75", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 2, position = position_dodge(-.7)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

ggsave("figures/fig_descriptives.pdf", 
       width = 10, height = 6,
       plot = fig_desc)
```

@@

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "activity", analysis = "regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "activity", analysis = "no controls")
dat_fig_results_activity_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "activity", analysis = "standardized")

@@

# safe figure
ggsave("figures/fig_results_activity.pdf", 
       width = 7, height = 4,
       plot = fig_results_activity)
```

@@

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "channels", analysis = "regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "channels", analysis = "no controls")
dat_fig_results_channels_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "channels", analysis = "standardized")

@@

# safe figure
ggsave("figures/fig_results_channels.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels)
```

@@

```{r}
# make figure
fig_results_control_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "control", analysis = "standardized"),
  sesoi = "std",
  legend = FALSE
  )
fig_results_control_std

# save figure
ggsave("figures/fig_results_control_std.pdf", 
       width = 7, height = 4,
       plot = fig_results_control_std)
```

>>>>

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey60", "grey75", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 1.5, position = position_dodge(-.7)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

ggsave("figures/fig_descriptives.png", 
       width = 10, height = 5,
       plot = fig_desc)
```

@@

```{r warning=FALSE}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "activity", analysis = "regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "activity", analysis = "no controls")
dat_fig_results_activity_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "activity", analysis = "standardized")

@@

# safe figure
ggsave("figures/fig_results_activity.png", 
       width = 7, height = 4,
       plot = fig_results_activity)
```

@@

```{r warning=FALSE}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "channels", analysis = "regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "channels", analysis = "no controls")
dat_fig_results_channels_std <- get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
                                            type = "channels", analysis = "standardized")

@@

# safe figure
ggsave("figures/fig_results_channels.png", 
       width = 7, height = 4,
       plot = fig_results_channels)
```

@@

```{r warning=FALSE}
# make figure
fig_results_control_std <- make_graph_res(
  get_dat_res(model_aff_neg_lmer_std, model_aff_pos_lmer_std, model_life_sat_lmer_std, 
              type = "control", analysis = "standardized"),
  sesoi = "std",
  legend = FALSE
  )
fig_results_control_std

# save figure
ggsave("figures/fig_results_control_std.png", 
       width = 7, height = 4,
       plot = fig_results_control_std)
```

### 2022-04-12 analyses_additional.Rmd
- implented reviewer feedback

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "activity", analysis = "1. regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "activity", analysis = "2. no covars")
dat_fig_results_activity_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "activity", analysis = "3. mean scores")
dat_fig_results_activity_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "activity", analysis = "4. no imp")
dat_fig_results_activity_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "activity", analysis = "5. mult imp")

dat_fig_results_activity <- rbind(
  dat_fig_results_activity,
  dat_fig_results_activity_nco,
  dat_fig_results_activity_m,
  dat_fig_results_activity_noi,
  dat_fig_results_activity_mim
)
# make figure
fig_results_activity <- make_graph_res(
  dat_fig_results_activity,
  sesoi = "est"
  )
fig_results_activity

# safe figure
ggsave("figures/fig_results_activity.pdf", 
       width = 7, height = 4,
       plot = fig_results_activity)
```

@@

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "channels", analysis = "1. regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "channels", analysis = "2. no covars")
dat_fig_results_channels_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "channels", analysis = "3. mean scores")
dat_fig_results_channels_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "channels", analysis = "4. no imp")
dat_fig_results_channels_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "channels", analysis = "5. mult imp")

dat_fig_results_channels <- rbind(
  dat_fig_results_channels,
  dat_fig_results_channels_nco,
  dat_fig_results_channels_m,
  dat_fig_results_channels_noi,
  dat_fig_results_channels_mim
)
# make figure
fig_results_channels <- make_graph_res(
  dat_fig_results_channels,
  sesoi = "est"
  )
fig_results_channels

# safe figure
ggsave("figures/fig_results_channels.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels)
```

>>>>

```{r warning=FALSE}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "activity", analysis = "1. regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "activity", analysis = "2. no covars")
dat_fig_results_activity_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "activity", analysis = "3. mean scores")
dat_fig_results_activity_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "activity", analysis = "4. no imp")
dat_fig_results_activity_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "activity", analysis = "5. mult imp")

dat_fig_results_activity <- rbind(
  dat_fig_results_activity,
  dat_fig_results_activity_nco,
  dat_fig_results_activity_m,
  dat_fig_results_activity_noi,
  dat_fig_results_activity_mim
)
# make figure
fig_results_activity_comparison <- make_graph_res(
  dat_fig_results_activity,
  sesoi = "est"
  )
fig_results_activity_comparison

# safe figure
ggsave("figures/fig_results_activity_comparison.pdf", 
       width = 7, height = 4,
       plot = fig_results_activity)
```

@@

```{r warning=FALSE}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "channels", analysis = "1. regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "channels", analysis = "2. no covars")
dat_fig_results_channels_m <- get_dat_res(model_aff_neg_lmer_m, model_aff_pos_lmer_m, model_life_sat_lmer, type = "channels", analysis = "3. mean scores")
dat_fig_results_channels_noi <- get_dat_res(model_aff_neg_lmer_noi, model_aff_pos_lmer_noi, model_life_sat_lmer_noi, type = "channels", analysis = "4. no imp")
dat_fig_results_channels_mim <- get_dat_res(model_aff_neg_lmer_mim, model_aff_pos_lmer_mim, model_life_sat_lmer_mim, type = "channels", analysis = "5. mult imp")

dat_fig_results_channels <- rbind(
  dat_fig_results_channels,
  dat_fig_results_channels_nco,
  dat_fig_results_channels_m,
  dat_fig_results_channels_noi,
  dat_fig_results_channels_mim
)
# make figure
fig_results_channels_comparison <- make_graph_res(
  dat_fig_results_channels,
  sesoi = "est"
  )
fig_results_channels_comparison

# safe figure
ggsave("figures/fig_results_channels_comparison.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels)
```
